CMSAC_reveal_js

### 2025-10-17 CMSAC_presentation/CMSAC_reveal_js.qmd
updated.

-   Comparing different structures like round robin and single eliminations, which is best?

-   Efficacy: Final rankings should match the true rankings of the strength of the competitors

-   Effectivity: Interested in correctly ranking the best competitor as first

CITEE

>>>>

-   Which competition structure is best at reflecting the true strengths of competitors?

-   **Efficacy**[^1]: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first

[^1]: Lasek and Gagolewsk (2018), Sziklai, Biró, and Csató (2022)

[^2]: Glenn (1960)
